2019 Draft Prep

### 2019-03-20 draftPrep.Rmd
Combined imports in progress

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(stop_on_error = 2L)
source("R/yahoo_api.R")
options(tidyverse.quiet=TRUE)
library(tidyverse)
```

@@

# Data Set
```{r importFangraphs, include=FALSE}
fangraphs_pitchers <- "data/fangraphs_pitchers.Rds"
fangraphs_batters <- "data/fangraphs_batters.Rds"
pitchers_file <- "data/depthChartProjections_pitchers_20190308.csv"
batters_file <- "data/depthChartProjections_batters_20190308.csv"

if (file.exists(fangraphs_pitchers) && file.exists(fangraphs_batters)) {
  pitchers <- readRDS(fangraphs_pitchers)
  batters <- readRDS(fangraphs_batters)
} else {
  if (!file.exists(pitchers_file) || !file.exists(batters_file)) {
  stop("Couldn't find fangraphs export data in the data folder")
}

  pitchers <- pitchers_file %>%
    read_csv() %>%
    unique() %>%
    select(playerid, 
           Name, 
           Team,
           ADP,
           IP,
           SV:ERA,
           SO,
           WHIP) %>%
    mutate(type = "pitcher")

  batters <- batters_file %>%
    read_csv() %>%
    unique() %>%
    select(playerid,
           Name,
           Team,
           ADP,
           PA,
           H,
           HR:SO,
           SB,
           OBP,
           OPS) %>%
    mutate(type = "batter")

  fangraphs <- pitchers %>% 
    bind_rows(batters)

  fangraphs$Name[fangraphs$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
  fangraphs$Name[fangraphs$Name == 'Cedric Mullins II'] <- "Cedric Mullins"
  fangraphs$Name[fangraphs$Name == 'Michael Soroka'] <- "Mike Soroka"
  fangraphs$Name[fangraphs$Name == 'Nathaniel Lowe'] <- "Nate Lowe"
  fangraphs$Name[fangraphs$Name == 'Nathan Karns'] <- "Nate Karns"
  fangraphs$Name[fangraphs$Name == 'Zach Britton'] <- "Zack Britton"
  fangraphs$Name[fangraphs$Name == 'Joshua James'] <- "Josh James"
  fangraphs$Name[fangraphs$Name == 'D.J. Stewart'] <- "DJ Stewart"

  batters <- fangraphs %>%
    filter(type="batter") %>%
    select(-type)

  pitchers <- fangraphs %>%
    filter(type="pitcher") %>%
    select(-type)

  batters %>% saveRDS(fangraphs_batters)
  pitchers %>% saveRDS(fangraphs_pitchers)
}

rm(c(fangraphs_pitchers, fangraphs_batters, pitchers_file, batters_file, fangraphs))
```

```{r importYahoo, include=FALSE}
yahoo_file <- "data/players_position_eligibility.Rds"
if (file.exists(yahoo_file)) {
  yahoo_players <- readRDS(yahoo_file)
} else {
  get_players(2500) -> yahoo_players

  position_columns <- yahoo_players %>%
    select(starts_with("eligible_positions")) %>%
    colnames()

  yahoo_players %>%
    mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
    mutate(positions = gsub('NA', '', positions)) %>%
    mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
    select(-(starts_with("eligible_positions"))) %>%
  select(name.full, display_position, positions) %>%
  mutate(name.full = chartr("áéóíñú", "aeoinu", name.full))  -> yahoo_players

  yahoo_players$name.full[yahoo_players$name.full == 'Daniel Vogelbach'] <- "Dan Vogelbach"
  yahoo_players$name.full[yahoo_players$name.full == 'Shohei Ohtani (Batter)'] <- "Shohei Ohtani"
  yahoo_players$name.full[yahoo_players$name.full == 'Shin-soo Choo'] <- "Shin-Soo Choo"
  yahoo_players$name.full[yahoo_players$name.full == 'Seunghwan Oh'] <- "Seung Hwan Oh"
  yahoo_players$name.full[yahoo_players$name.full == 'JT Riddle'] <- "J.T. Riddle"
  yahoo_players$name.full[yahoo_players$name.full == 'AJ Reed'] <- "A.J. Reed"

  yahoo_players %>% 
    saveRDS(yahoo_file)
}
rm(yahoo_file)
```
